\documentclass[10.5pt,a4paper]{article}

% --------------------
% Packages
% --------------------
\usepackage[margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

% --------------------
% Formatting
% --------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\titleformat{\section}
  {\bfseries\large}
  {}
  {0pt}
  {}

\titleformat{\subsection}
  {\bfseries}
  {}
  {0pt}
  {}

% Tight lists
\setlist[itemize]{
  leftmargin=1.1em,
  itemsep=2pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

% --------------------
% Document
% --------------------
\begin{document}

% --------------------
% Header
% --------------------
{\Large \textbf{Simon Neumeyer}} \\[-2pt]
Barcelona / Zurich \\
+34 650 51 64 90 ·
\href{mailto:simon.funkneumeyer@gmail.com}{simon.funkneumeyer@gmail.com}

\vspace{6pt}

\vspace{4pt}
\textbf{Senior Data Scientist / Data Engineer with 6+ years of experience building robust, production-grade
Python data pipelines for analytics, machine learning, and AI systems. Strong background in
large-scale data ingestion, transformation, and feature engineering across structured and
unstructured data, supporting downstream ML, computer vision, and emerging LLM-based
workflows in cloud environments.}

\vspace{1pt}
% --------------------
% Experience
% --------------------
\section*{Professional Experience}

\subsection*{The World Bank Group --- Data Scientist}
Barcelona, Spain \hfill 04/2021 -- Present
\newline
\textbf{Built and maintained end-to-end data pipelines for large-scale analytics and applied machine learning (including computer vision, geospatial data science) supporting impact evaluations in transport, mobility, and financial inclusion projects.}
\begin{itemize}
    \item \textbf{Public transit experiment (Lagos, Nigeria):} developed daily ingestion and analytics pipelines to track usage patterns and performance metrics.
    \item \textbf{Global decarbonization project:} worked with $>$100TB of geospatial mobility data to estimate average daily travel distances across $\sim$120 countries.
    \item \textbf{Road safety impact evaluation (Addis Ababa):} applied computer vision and ML (YOLO, DeepSORT) to extract behavioral metrics from video data.
    \item \textbf{Credit impact evaluation (Kosovo):} applied ML and statistical analysis to identify drivers of access to credit and predict potential MSME borrowers.
    \item Collaborated with cross-functional teams to translate analytical results into reusable data products and insights for complex, data-driven projects.
\item \textbf{Generative AI \& LLMs:} completed advanced online training to bridge classical ML expertise with recent GenAI developments (Prompting, embeddings, fine-tuning, RLHF, RAG-style pipelines)

\end{itemize}

\subsection*{Novartis --- Data Scientist}
Barcelona, Spain \hfill 10/2021 -- 04/2022
\begin{itemize}
    \item Rewrote and refined internal cost-prediction models, improving robustness, interpretability, and alignment with business metrics.
\end{itemize}

\subsection*{The Boston Consulting Group (BCG) --- Data Scientist}
Barcelona, Spain \hfill 04/2019 -- 09/2020
\begin{itemize}
    \item Applied optimization, forecasting and statistical modeling to pricing, demand, and performance problems for large clients.
    \item Projects included grocery price modeling and COVID-era demand forecasting for a leading beauty retailer.
    \item Translated ambiguous business questions into structured analytical problems and executive-ready insights.
\end{itemize}

\subsection*{Pompeu Fabra University \& IESE Business School --- Research Assistant}
Barcelona, Spain \hfill 06/2018 -- 04/2019
\begin{itemize}
    \item Built and trained machine-learning models (including RNNs in Python) and prepared large datasets for applied research in economics and behavioral analysis.
\end{itemize}

% --------------------
% Education
% --------------------
\section*{Education}

\subsection*{Barcelona School of Economics --- Barcelona, Spain}
\textbf{MSc in Data Science} \hfill 09/2020 -- 07/2021 \\
GPA: 8.4 / 10 (Excellent)
\begin{itemize}
    \item Core coursework in Machine Learning, Statistical Modeling, Discrete \& Continuous Optimization.
    \item Advanced econometrics and causal inference: panel regression, time series, IV, DiD, RDD, etc.
    \item Strong implementation focus: built models and estimators from scratch in Python rather than relying on black-box libraries.
\end{itemize}

\subsection*{Barcelona School of Economics --- Barcelona, Spain}
\textbf{MSc in Economics} \hfill 09/2017 -- 07/2018 \\
GPA: 8.1 / 10 (Excellent)
\begin{itemize}
    \item Master's thesis: \href{https://thevoice.bse.eu/2018/09/03/spillover-effects-financial-sector-network-analysis-eurozone/}{Spillover Effects from the Financial Sector: A Network Analysis for the Eurozone} (9.5/10), published in UPF repositories; summary featured by the Barcelona School of Economics.

\end{itemize}

\subsection*{University of Zurich --- Zurich, Switzerland}
\textbf{BA in Economics} \hfill 09/2013 -- 04/2017 \\
GPA: 5.1 / 6 (Magna Cum Laude)
\begin{itemize}
    \item Bachelor thesis: \textit{Innovation and Top Income Inequality -- A European Study} (6/6).
\end{itemize}

% --------------------
% Skills
% --------------------
\section*{Languages \& Technical Skills}

\textbf{Languages:} German (Native), English (Fluent), Spanish (Professional), French (Intermediate) \\

\textbf{Technical Skills:} Python, SQL, AWS (S3, SageMaker), Git, Shell, R, Stata, QGIS;
Generative AI \& LLMs (prompt engineering, embeddings, fine-tuning, retrieval-augmented generation)


% --------------------
% Additional
% --------------------
\section*{Additional Information}

\begin{itemize}
    \item BSE partial tuition fee waiver for MSc Data Science (academic merit).
    \item 3rd prize winner, Novartis Datathon 2020 (60+ international teams).
    \item Swiss nationality.
\end{itemize}

\end{document}
